---
title: "ANCOVA homeowkr"
author: "Sarah"
date: "25/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For your homework you are going to be running a GLM with one categorical and one continuous (numerical) predictor. The data are from a study testing the hypothesis that people are more comfortable with potentially infectious contact with people they like ( https://journals.sagepub.com/doi/full/10.1177/0956797620960011). Comfort with contact was measured with 10 items measuring how comfortable the participant was with different forms of potentially contaminating contact e.g. "Touching a handkerchief that [target] used to blow his or her nose.” Participants rated each item on a scale from −3 (very uncomfortable) to 3 (very comfortable). Each participant was told to think about a person with which they had one specific type of relationship (1 = romantic partner, 2 = closest friend, 3 = acquaintance, 4 = enemy). Additionally participants completed a disgust sensitivity measure to determine how cautious about infection they were in general. Disgust sensitivity is used as a covariate in the analysis.  

```{r}
library('tidyverse')
```

Download the data from Moodle and read it in by running the code below:
```{r}
infection <- read.csv("data/infection.csv")
```

1. Calculate each participant's mean score on the comfort scale by first gathering the data into long format and then calculating the mean 

```{r}
indvdl_mean_comf <- infection %>% gather(Comfort_Item, Value, comf1:comf10) %>% group_by(participant) %>% summarise(indvdl_mean_comf=mean(Value))
```

2. Calculate each participant's mean score on the disgust sensitivity scale using the same method. 

```{r}
indvdl_mean_DS <- infection %>% gather(DS_Item, Value, DS1:DS7) %>% group_by(participant) %>% summarise(indvdl_mean_DS=mean(Value))
```

3. Merge the two mean score variables back into the infection dataset 

```{r}
infection <- inner_join(infection, indvdl_mean_comf, by='participant') %>% inner_join(indvdl_mean_DS, by='participant')
```

4. Each participant was told to think about one type of relationship whilst completing the comfort questions. Recode the values in relationship_category to the following labels: "1.romantic partner", "2.closest friend", "3.acquaintance", "4.enemy"

```{r}
infection <- infection %>% mutate(relationship_category=recode(relationship_category,"1"="romantic partner","2"="closest friend", "3"="acquaintance", "4"="enemy"))
```

5. Graph the relationship between relationship category and comfort

```{r}
summary_table <- infection %>% drop_na() %>% group_by(relationship_category) %>% summarise(mean_comf=mean(indvdl_mean_comf))
  
ggplot(summary_table, aes(x=relationship_category, y=mean_comf)) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x="Relationship Category",y="Mean Comfort") +
  theme_bw()
```

6. Graph the relationship between disgust sensitivity and comfort. 

```{r}
ggplot(infection, aes(x=indvdl_mean_DS, y=indvdl_mean_comf)) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x="Disgust Sensitivity",y="Comfort") +
  theme_bw()
```

7a. Run a GLM with relationship category predicting comfort

```{r}
mod_1IV <- lm(indvdl_mean_comf~relationship_category, dat=infection)

summary(mod_1IV)
```

7b. Does relationship predict comfort with contact? How do you know?

Relationship Category seems to predict comfort with contact, with p-values of all 4 relationship categories being significant (p<.05)

8a. Now run a GLM with relationship and disgust sensitivity predicting comfort 

```{r}
mod_2IV <- lm(indvdl_mean_comf ~ relationship_category + indvdl_mean_DS, dat=infection)

summary(mod_2IV)
```

8b. How much variance does this model explain? Does this suggest it is a better model than the model with only relationship sensitivity? 

This model explains 60% of the variance in the data (comfort with contact). This is greater than the variance explained by the previous model (57%), which suggests that this model is better than the model with only relationship sensitivity as predictor.

9a. To formally test whether adding disgust sensitivity improves the model, compare these two models using the anova() function 

```{r}
anova(mod_2IV, mod_1IV)
```

9b. What do the results of the model comparison tell you?

There results tell us that the larger model (model 1 in the output, called mod_2IV) is a significantly better fit than the smaller model (model 2 in the output, called mod_1IV), since p<.05.


