---
title: "Week 6: Alpha, Power and Effect Sizes Homework"
output:
  html_document: default
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# install.packages("pwr")
library(pwr)
library(tidyverse)
```

### Tasks using power analysis

1. What is the power to detect an effect size of .33 in a between (= two-sample) samples t-test with 60 in each group and alpha of .05. Is this adequate?

```{r echo=FALSE, eval=FALSE}
pwr.t.test(n=60, d=0.33, sig.level = .05, type='two.sample')
```
This is not adequate since our resulting power is only about 43%, which means that, with these parameters, we only hold 43% power to be able to detect the effect, even if the effect truly existed.


2. How many would be needed in each group to obtain a power of 80% with this design?

```{r echo=FALSE, eval=FALSE}
pwr.t.test(power=.8, d=0.33, sig.level = .05, type='two.sample')
```
With this experimental design, we would need 146 participants (rounded up) in each group to obtain a 80% power to detect the effect.

3. What effect size would you have at least 90% power to detect if you had a sample of 20 in a paired t-test?

```{r echo=FALSE, eval=FALSE}
pwr.t.test(n=20, power=.9, type='paired')  # default sig.level = .05
```
With this experimental design, you would only be able to detect effect sizes of 0.76 and above with a power of 90%.

4. To seek a 0.5 effect size with 80% power in an independent t-test, with alpha of .01, how many participants would you need in each group?

```{r echo=FALSE, eval=FALSE}
pwr.t.test(d=0.5, power=.8, sig.level = .01, type='two.sample')
```
With this experimental design, you would need 96 (rounded up) participants in each group.

5. Create a power curve graph for the following experiment:

Sample size of between 15 and 75 per group, going up in increments of 5.
Effect sizes of .3, .6 and .9
Alpha fixed at .05
Two sample t-test.

```{r}
# create a function outputing the power given some parameters about the experimental design
get_power <- function(df){
  power_result <- pwr.t.test(n=df$sample_sizes, 
                             d=df$effect_sizes,
                             sig.level = .05,
                             type='two.sample')
  df$power=power_result$power
  return(df)
}

# setting remaining parameters (with ranges) and creating the df input to the power curve
effect_sizes <- c(.3, .6, .9) # 3 different significance levels
sample_sizes = seq(15, 75, 5) # going from 0 to 200 in increments of 5
input_df <- crossing(effect_sizes, sample_sizes)

# creating our power curve on our input df
power_curves <- get_power(input_df)
power_curves <- power_curves %>% mutate(effect_sizes = as.factor(effect_sizes)) 

# plotting the power curve
ggplot(power_curves, aes(x=sample_sizes, y=power, linetype=effect_sizes)) + 
  geom_line() + 
  geom_hline(yintercept = 0.8, color='green') +
  theme_light() + 
  labs(title='Power Curve for fixed alpha of .05 (two samples t-test)')
  ggsave('power_curve_hwk6.jpg')

```

6. Draw a horizontal line to mark where 80% power is, and estimate the required sample size, assuming an effect size of .9

We created the horizontal line to in the previous code cell, using the geom_hline() function.
Assuming an effect size of .9 (predicted), for a significance level of .05 in a two sample-test, we would need 20 participants in each group to hold 80% power to detect the effect, if it truly exists.

7. With an assumed effect size of .6, would there be any point seeking a sample size greater than 50 per group?

Assuming an effect size of .6, for a significance level of .05 in a two sample-test, we would need approx 45 participants in each group to hold 80% power to detect the effect, if it truly exists. In this sense, if we are satisfied with a 80% power, which is typically considered as an 'adequate' amount of power, then we would have no problem in having a sample size of 50 participants per group, which leads to a power just above 80%. However, this is left to the decision of the researcher. Indeed, they could be willing to increase their power beyond the generally accepted percentage value of 80%, as increasing power never hurts. But, if it is practically difficult to increase the power beyond 80-85% because of, for example, difficulty in recruiting more participants (costly, time-consuming, or plainly impossible), then it is okay to proceed with the experiment with 50 participants per group; in this sense, there may be no point in seeking a sample size greater than 50 per group, given our satisfaction with an 80% power and/or the impossibility to recruit more participants (if we were willing to hold a >80% power).







