---
title: "week12 homework"
author: "Jo Saul"
date: "19/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1 type this code to load the dataset. Ensure you have any packages needed for factor analysis loaded.
```{r q01}
data(bfi)

library(tidyverse)
library(broom)
library(psych)
```


#2 use ?bfi to find out about the dataset, the items and how they are scored
```{r q02}
?bfi
```

#3 remove unneeded columns: select only A1:C5
```{r q03}
data <- bfi %>% select(A1:C5)

```

#4 items A1 and C3:5 are reverse scored - we can transform them to make interpretation easier. HINT: answer to A1 = 7-Answer
```{r q04}
data <- data %>% mutate(A1=7-A1,
                        C3=7-C3,
                        C4=7-C4,
                        C5=7-C5
                        )

```

#5 are there any missing data - if so remove
```{r q05}
data <- data %>% drop_na()

```

#6 are the data z-scores, if not scale them
```{r q06}
data_Zscores <- data %>% scale() 

```

#7 Review the correlations of these indicators.
```{r q07}
cor_matrix <- data %>% cor()

```

#8 look at screeplot to determine how many factors to extract.

```{r q08}
# scree plot: how many factors do we extract?
scree(data_Zscores, pc=F)  # F: deselect principal components since we are interested in factors

# If we use the 'eigenvalues > 1' rule of thumb, the scree plot below suggests that we should extract 2 factors.
```

#9. What is the KMO for this dataset and is it sufficient for a factor analysis
```{r q09}
KMO(cor(data_Zscores))

# The KMO for this dataset is .78, i.e. greater than .60, which is sufficient to run a factor analysis. 
```


#10.conduct an exploratory factor analysis on this dataset
```{r q10}
fit <- factanal(data_Zscores, factors=2, scores='regression')

print(fit)
fit$STATISTIC
fit$PVAL

```

#11. how much variance is explained? 


```{r q11}
# Factor 1 and Factor 2, i.e. 2 factors, explained 36.4% of the variance in the dataset.
```


#12. tabulate the factor scores - do scores on factor 1 and 2 correlate with each other - if so describe the relationship.
```{r q12}
scores <- fit$scores %>% as.data.frame()

data_Zscores <- data_Zscores %>% as.data.frame() %>% mutate(f1=scores$Factor1, f2=scores$Factor2)

# correlations
cor(data_Zscores)

# There is a small positive correlation between Factor 1 and Factor 2 (.09).
```


