---
title: "hello"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Date: 07/10/2020

## R Markdown

Step 1 - Set-Up
```{r}
install.packages('tidyverse')
```

```{r}
install.packages('broom')
```

```{r}
library('tidyverse')
library('broom')
```

```{r}
ratings = read.csv('voice_ratings.csv')

acoustics = read.csv('voice_acoustics.csv')
```


Step 2 - Data Wrangling
```{r}
ratings_tidy <- ratings %>% gather(participant, rating, P1:P28)
```

```{r}
ratings_mean <- ratings_tidy %>% group_by(VoiceID) %>% summarise(mean_ratings=mean(rating))
```

```{r}
joined <- inner_join(ratings_mean, acoustics, by='VoiceID')
```

```{r}
joined_wide <- spread(joined, 'measures', 'value')
```

Best Practice:
```{r}
rm(acoustics, joined, ratings, ratings_mean, ratings_tidy)
```


Step 3 - Descriptive Statistics
```{r}
summary_table <- joined_wide %>% group_by(sex) %>% summarise(num_voices=n(), mean_trust_rating=mean(mean_ratings), sd_trust_rating=sd(mean_ratings), se_trust_rating=sd_trust_rating / sqrt(num_voices), CI_95_trust_rating_low=mean_trust_rating - (1.96 * se_trust_rating), CI_95_trust_rating_upper=mean_trust_rating + (1.96 * se_trust_rating))
                                                             
```

Step 4 - Data Visualisation
```{r}
ggplot(joined_wide, aes(x=mean_ratings)) +
  geom_histogram()+
  theme_bw()
```

Scatter Plot
```{r}
ggplot(joined_wide, aes(x=Pitch, y=mean_ratings)) +
  geom_point() +
  geom_smooth(method='lm') +
  facet_wrap(~sex) +
  labs(title='Relationship between Pich and Trustworthiness (by sex)')
```


Box Plot
```{r}
ggplot(joined_wide, aes(x=sex, y=Dispersion)) +
  geom_violin() +
  geom_boxplot(width=0.1)
```

Step 5 - Inferential Statistics: t-test
```{r}
var.test(joined_wide %>% filter(sex=='M') %>% pull(mean_ratings), 
         joined_wide %>% filter(sex=='F') %>% pull(mean_ratings))
```
p > 0.05 so our p-value is not significant and therefore we cannot reject the null hypothesis that variances are equal.
From now on, we consider variances equal.

```{r}
trust_mean_rating_t <- t.test(joined_wide %>% filter(sex=='M') %>% pull(mean_ratings), joined_wide %>% filter(sex=='F') %>% pull(mean_ratings), var.equal=TRUE) %>%
  
  tidy()
```
The t-statistic is approximately equal to -1.31, while the p-value is approximately equal to 0.195. 
p > 0.05, so we did not obtain a signficant result.
t(62) = -1.31, p =0 .195.


Step 6 - Inferential Statistics: correlation


A) Assumptions for Pearson's Correlation

1/ trustworthiness rating (`mean_ratings`) is interval and pitch is ratio data.

2/ we have datapoints for both variables.

3/ trustworthiness seems to be normally distributed (histogram created earlier).

4/ pitch also seems to be normally distributed:
```{r}
ggplot(joined_wide, aes(x=Pitch)) +
  geom_histogram(bins=30)+
  theme_bw()
```

5/ there seems to be a linear relationship between trustworthiness rating (`mean_ratings`) and pitch:
```{r}
ggplot(joined_wide, aes(x=Pitch, y=mean_ratings)) + 
  geom_point() +
  theme_bw()
```

6/ homoscedasicity

Definition (Practical 13 in Year 1): it is that the spread of datapoints around the (imaginary) line of best fit is even on both sides along the line; as opposed to very narrow at one point and very wide at others. 

Yes.


B) Running Correlation: separately for each sex

# Correlation for Males' Pitch
```{r}
cor_male_results <- cor.test(joined_wide %>% filter(sex=='M') %>% pull(Pitch), joined_wide %>% filter(sex=='F') %>% pull(mean_ratings)) %>%
  
  tidy()
```

Testing the hypothesis that there would be a relationship between trustworthiness rating (mean_ratings) and pitch in men, a pearson correlation found a significant relationship between the mean ratings of trustworthiness for voices and male pitches, r(30) = -3.081, p = 0.004. 


# Correlation for Females' Pitch
```{r}
cor_female_results <- cor.test(joined_wide %>% filter(sex=='F') %>% pull(Pitch), joined_wide %>% filter(sex=='F') %>% pull(mean_ratings)) %>%
  
  tidy()
```

Testing the hypothesis that there would be a relationship between trustworthiness rating (mean_ratings) and pitch in women, a pearson correlation found NO significant relationship between the mean ratings of trustworthiness for voices and female pitches, r(30) = -0.150, p = 0.881. 


Clean-Up 
```{r}
rm(cor_results)
```











