---
title: "Practical 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)

library(ez)
```

The Data
```{r}
milktea<-tibble(id=1:12,milk=rep(c("No","Yes"),each=6),
                teatype=rep(rep(c("Green","Black"),each=3),2),
            deliciousness=c(74, 65, 77, 70, 74, 66, 67, 67, 64, 78, 78, 84))
```


Plotting the interaction
```{r}
# 1
summary_table <- milktea %>% group_by(milk, teatype) %>% summarise(mean_ratings= mean(deliciousness),
                                       sd_ratings=sd(deliciousness),
                                       se_ratings=sd_ratings/sqrt(n()),
                                       CI_95_lower=mean_ratings - 1.96*se_ratings,
                                       CI_95_upper=mean_ratings + 1.96*se_ratings)
                              

```

```{r}
# 2
ggplot(summary_table, aes(x=milk, y=mean_ratings, group=teatype, colour=teatype)) +
  geom_line(stat='identity') +
  geom_errorbar(aes(ymin = CI_95_lower, ymax = CI_95_upper, colour=teatype), width=0.2) +
  labs(title='Plot of the ratings of tea deliciousness (mean) as a function of milk', x='milk', y='mean') +
  scale_color_manual(labels = c('Black', 'Green'), values = c('black', 'green'))
  theme_classic() 
 
```


Looking at the interaction plot what do you think we are going to find in our two-way ANOVA?

ANSWER: There seems to be an interaction effect between the tea type and whether there was milked poured or not. Indeed, the teatype factor seems to depend on the milk factor (or we could have said the converse, same).
Therefore, I think we will find an interaction between milk and tea type: we will find a main effect of teatype depending on milk/no milk. Only when pouring milk (milk=Yes), there a difference between black and green tea types. 


Estimation equations and decomposition matrix
```{r}
dmx<- milktea %>% mutate(i=recode(milk,Yes=1,No=2),
                         j=recode(teatype,Green=1,Black=2),
                         k=rep(1:3,4),
                         Y_ijk=deliciousness,
                         mu = mean(Y_ijk)) %>%
                           group_by(i) %>% mutate(A_i = mean(Y_ijk) - mu) %>%
                           group_by(j) %>% mutate(B_j = mean(Y_ijk) - mu) %>%
  select(-milk,-teatype,-deliciousness,-id)
```


Adding the missing columns
```{r}
dmx2 <- dmx %>% group_by(i,j) %>% mutate(AB_ij = mean(Y_ijk) - mu - A_i - B_j)
dmx2 <- dmx2 %>% ungroup() %>% mutate(err=Y_ijk - mu - A_i - B_j - AB_ij)
```


Calculate F and p values for the main effects and interactions from the decomposition matrix
```{r}
# 1: Sum of Squares (SS)
sstable <- dmx2 %>% summarise(ssA=sum(A_i^2),
                              ssB=sum(B_j^2),
                              ssAB=sum(AB_ij^2),
                              sserr=sum(err^2))
```

```{r}
# 2: Means of Sum of Squares (MSS)

## degrees of freedom
df_A = 2 - 1
df_B = 2 - 1
df_AB = df_A * df_B 
df_error = 12 - 4   # total num of participants - num of groups

mstable <- sstable %>% summarise(msA = ssA / df_A, 
                                 msB = ssB / df_B,
                                 msAB = ssAB / df_AB,
                                 mserr= sserr / df_error)
```

```{r}
# 3: F values
F_table <- mstable %>% summarise(F_A=msA/mserr,
                                 F_B= msB/mserr,
                                 F_AB= msAB/mserr)
```

```{r}
# 4: p-values

p_table <- F_table %>% summarise(p_A = pf(F_A, df_A, df_error, lower.tail = FALSE),       # p value for the effect of milk (A)
                                 p_B = pf(F_B, df_B, df_error, lower.tail = FALSE),       # p value for the effect of tea type (B)
                                 p_AB = pf(F_AB, df_AB, df_error, lower.tail = FALSE)) # p value for the interaction (AB)


```
See if you can describe our results for the main effects of milk, main effect of tea and and the interaction.

ANSWER: from the p table we created with the 3 p-values, we can see that there seems to be a significant interaction (AB) between milk (A) and tea type (B) as p <.05, a main effect of tea (B) (p<.05), but no main effect of milk (A) (p>.05).


Do it the easy way using ezANOVA()
```{r}
# reminder: check the 2nd table (not the third one, the third one outputs the Levene's test results)

ezANOVA(data=milktea,
        dv=deliciousness,
        wid=id,
        between=c(milk, teatype),
        detailed = TRUE)
```

# Report

“A 2 x 2 between subjects ANOVA found a significant main effect of tea type, F(1,8) = 6.17, p = 0.0379, ges = 0.435 but not milk, F(1,8) = 0.69, p = 0.4316, ges = 0.079 on drink deliciousness ratings. The interaction between tea type and milk was significant F(1,8) = 10.97, p = 0.0107, ges = 0.578 with black tea being rated as MORE delicious with milk than without milk, and green tea being rated as LESS delicious with milk than without milk.”








