---
title: "Homework: Week 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Complete each code chunk below by deleting #ADDCODE and entering the correct code. Run each code chunk to check that it is working before you submit. 

There is an optional 10th question for those of you that want a challenge. Give this a go but don't worry if you can't work it out- we will go through the answer at the start of next week. 

Remember to set the working directory to where the happiness data files are stored before you start.

Question 1: load the tidyverse package
```{r}
#load tidyverse
install.packages("tidyverse")
 
```

Question 2: Use read.scv to load in the participant info and questionnaire response datasets and call them 'pinfo' and 'responses'
```{r}
#load participant info and questionnaire responses 
pinfo<-read.csv("participant-info.csv")
responses<-read.csv("ahi-cesd.csv")
```

Question 3: Join the participant info and responses data together using inner_join
```{r}
#join the pinfo and responses
all_data<-inner_join(responses,pinfo,by= c('id','intervention'))
```

Question 4: Create new dataframe with just id, age, ahiTotal, cesdTotal, educ and occasion variables using select()
```{r}
#select id, age, ahiTotal, cesdTotal, educ and occasion variables
selected_vars <- select(all_data, id, age, ahiTotal, cesdTotal, educ, occasion)
```

Question 5: Create new dataframe called 'pre' with only observations from pre intervention test (e.g. occasion 1) using filter()
```{r}
#occasion 1 data only 
pre <- filter(selected_vars, occasion == 1)
```

Question 6: Create new age_asc dataframe containing rows from pre dataframe arranged by age with lowest age first.
```{r}
#arrange by age
age_asc<-arrange(pre, by= age)
```

Question 7: Use sumarise() to create a new object called ahimedian, which contains the median ahiTotal score.HINT: the code median() calculates the median and works in the same way as mean()
```{r}
#Calculate median ahiTotal score.
medianAHI<-summarise(pre, ahimedian=mean(ahiTotal))
```

Question 8: Create a new data frame called pre_edu containing pre data grouped by the education level variable
```{r}
#Group by education level
pre_edu <- group_by(pre, educ)
```

Question 9: Use summarise to create a new object called pre_edu_median containing median ahi for each education level
```{r}
#calculate median ahiTotal for each education level
pre_edu_median <- summarise(pre_edu, medianAHI)
```

Optional challenge: Try using mutate(), if_else() and mean() to create a new variable called happiness_split that codes whether each participant has 'above' or 'below' average levels of happiness (ahiTotal). HINT: you will need the logical operator for greater than ```>```. 

```{r}
#create happiness split variable
pre<-mutate(pre, happiness_split = if_else(ahiTotal>mean(ahiTotal), "above","below"))
```
