---
title: "Practical 6"
author: "Dilay Fidan Ercelik"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Set Up
```{r}
install.packages('pwr')
library(pwr)

library(tidyverse)
```


Part 1. Power analysis


# 1. Determining sample size required for a given power

```{r}
# default sig.level = .05 
pwr.t.test(d=0.5, power=.8)
```
Thus, about 64 participants would be needed in each group in order to test the hypothesis with adequate power (80%) at alpha of .05.


```{r}
# sig.level = 0.01
pwr.t.test(d=0.5, power=.8, sig.level = 0.01)
```
This increases group size to 95.



# 2. Determining the power to detect effect sizes, given a specific sample size

```{r}
pwr.t.test(n=75, d=0.5) 
```
With 75 participants in each group, a two sample t-test has 86% power to detect an effect of .5, given alpha of .05.


There are different options depending on the study design. If it is a one sample t-test, you use the parameter type='one.sample' or if it is a paired t-test you type type='paired'. The default is type='two.sample' for an independent t-test.

```{r}
# one sample t-test
pwr.t.test(n=75, d=0.5, type='one.sample') 
```
Using 75 participants in a one sample t-test, with alpha of .05 and assumed effect size of .5, the resulting power is 99%.


# 3. Determining the minimum effect size that a specific sample can detect with a specific power

```{r}
pwr.t.test(n=75, power=.9, sig.level=.01,  type='one.sample')
```
Using 75 participants in a one sample t-test, with alpha of .01 and required power of 90%, you have the power to detect an effect size of .46 and above.


# Tasks using power analysis

1. Try to consider whether a paired or 2 sample t-test would give the highest power if all else was equal. Then run some code to find out.
```{r}
# paired
pwr.t.test(n=75, d=0.5, type='paired')   # higher power than in two sample t-test
```

```{r}
# two-sample
pwr.t.test(n=75, d=0.5, type='two.sample')
```

Higher power in paired t-test than in two-sample independent t-test because samples are more similar in the paired t-test (same participants).


2. Run the code for an independent t-test with 25 in each group, expecting to find an effect size of 1.0 - what is the power, if your alpha level was 0.01?
```{r}
pwr.t.test(n=25, d=1, sig.level = 0.01)  
```
Power = 80%


3. What effect size would you have at least 80% power to determine if you had a sample of 50 in a one sample t-test?
```{r}
pwr.t.test(n=50, power=.8, type='one.sample')  # sig.level = .05
```
Min Effect Size detectable = 0.4


4. To seek a 0.5 effect size with 90% power in a paired t-test, how many participants would you need?
```{r}
pwr.t.test(d=0.5, power=.9, type='paired')   # sig.level = .05
```
N of Participant Pairs needed: 44



Part 2. Power Curves


```{r}
effect_sizes <- c(0.25, 0.5, 0.75) # 3 different effect sizes

sample_sizes = seq(10, 500, 10) # going from 10 to 500 in increments of 10

input_df <- crossing(effect_sizes,sample_sizes)

head(input_df)
```
Using this, we can then perform a power analysis for each combination of effect size and sample size to create our power curves. In this case, let’s say that we wish to perform a two-sample t-test.

```{r}
# new get_power function: return the power of a given set of sample and effect sizes, saved in a dataframe df

get_power <- function(df){
  power_result <- pwr.t.test(n=df$sample_sizes, 
                             d=df$effect_sizes)
  df$power=power_result$power
  return(df)
}

```

```{r}
power_curves <- get_power(input_df) 

head(power_curves)
```
Before we plot the power curve we need to convert effect_size to a factor so it can be a grouping variable

```{r}
power_curves <- power_curves %>% mutate(effect_sizes = as.factor(effect_sizes)) 
```

```{r}
ggplot(power_curves, aes(x=sample_sizes, y=power, linetype=effect_sizes)) + 
  geom_line() + 
  geom_hline(yintercept = 0.8, color='green') +
  theme_light() +
  ggsave('power_curve.jpg')
```
- required sample size for each effect size to reach 80% power:
    for d = 0.25, n = 250
    for d = 0.5, n =  60 approx
    for d = 0.75, n = 30 approx
    
- If you are seeking a .75 effect size, is there any incremental benefit in power once your sample size reaches 100?
Not for effect sizes 0.5 and 0.75



Part 3. Simulating statistical power


1. 
```{r}
effectSize <- 0.5
```

2.
```{r}
pwr.result <- pwr.t.test(d=effectSize, power=.8)

# round up from estimated sample size
sampleSize <- ceiling(pwr.result$n)    # 64
```

3. 
```{r}
get_t_result <- function(sampleSize, effectSize){
  group1 <- rnorm(sampleSize) # normal sample with mean of 0, sd of 1
  group2 <- rnorm(sampleSize, mean=effectSize) # normal sample with mean of effect size, sd of 1
  ttest.result <- t.test(group1, group2) #carry out a t-test
  return(tibble(pvalue=ttest.result$p.value)) # return the p-value
}
```

4.
```{r}
get_t_result(sampleSize, effectSize)
```

5. 
```{r}
nRuns <- 1000
```

6.
```{r}
index_df <- tibble(id=seq(nRuns)) %>%
  group_by(id) #this group_by() command is so that the function runs for each simulation

power_sim_results <- index_df %>%
  do(get_t_result(sampleSize, effectSize)) #this runs the get_t_result function for the index_df table

power <- power_sim_results %>% ungroup() %>% summarize(pvalue = mean(pvalue<.05)) %>% pull()

power
```


# Tasks with simulation

Create a similar simulation for an effect size of .6, a significance level of 0.01 and a power of 90%. This time use 5000 simulations

```{r}
effectSize <- 0.6

pwr.result <- pwr.t.test(d=effectSize, power=.9, sig.level = 0.01)
sampleSize <- ceiling(pwr.result$n)

get_t_result(sampleSize, effectSize)

nRuns <- 5000

index_df_2 <- tibble(id=seq(nRuns)) %>%
  group_by(id) #this group_by() command is so that the function runs for each simulation

power_sim_results_2 <- index_df_2 %>%
  do(get_t_result(sampleSize, effectSize)) #this runs the get_t_result function for the index_df table

power_2 <-
  power_sim_results_2 %>%
  ungroup() %>% #this 
  summarize(pvalue = mean(pvalue<.05)) %>%
  pull()

power_2   # pvalue output = 4.55e-06


```



# EXTENSION TASK

1. Going back to part 2 (power curves), modify the get_power() function to show power to find a fixed effect size (d=0.5) for a range of significance levels (0.05, 0.01, 0.001) and sample sizes (from 0 to 200 in increments of 5) and then graph them up as before. Study design is paired t-test. HINT: use the crossing() function to make your table of inputs

ANSWER: 
```{r}
get_power_extension <- function(df){
  power_result <- pwr.t.test(n=df$sample_sizes, 
                             d=0.5,
                             sig.level = df$significance_levels,
                             type='paired')
  df$power=power_result$power
  return(df)
}
```

```{r}
significance_levels <- c(0.05, 0.01, 0.001) # 3 different significance levels

sample_sizes = seq(0, 200, 5) # going from 0 to 200 in increments of 5

input_df_extension <- crossing(significance_levels, sample_sizes)

head(input_df_extension)
```
```{r}
power_curves_extension <- get_power_extension(input_df_extension) 

head(power_curves_extension)
```

```{r}
power_curves_extension <- power_curves_extension %>% mutate(significance_levels = as.factor(significance_levels)) 
```

```{r}
ggplot(power_curves_extension, aes(x=sample_sizes, y=power, linetype=significance_levels)) + 
  geom_line() + 
  geom_hline(yintercept = 0.8, color='green') +
  theme_light() + 
  labs(title='Power Curve for fixed effect size of 0.5 (paired samples t-test)')
  ggsave('power_curve_extension_task.jpg')
```


2. Reading from the graph, what sample size is needed if one assumes an alpha level of 0.001 at 80% power?

ANSWER: sample size needed if one assumes an alpha level of 0.001 at 80% power, for an effect size of 0.5, is: 75 






