---
title: "Practical 12 - Factor Analysis"
author: "Dilay Fidan Ercelik"
date: "1/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Task 1 - Set Up
```{r}
library(tidyverse)
library(broom)
library(psych)
```

```{r}
dat1 <- read_csv('data/dat1.csv')
```


Task 2 - Exploring the dataset
```{r}
# summary table of means and sds
summary <- dat1 %>% gather(Item, Score, V1:V6) %>% group_by(Item) %>% summarise(Mean=mean(Score), SD=sd(Score))
```

```{r}
# correlation matrix
corr_matrix <- dat1 %>% select(!X1) %>% cor()
```


Task 3 - Testing assumptions
```{r}
# transforming into z-scores
dat1 <- dat1 %>% select(!X1) %>% scale()
```

```{r}
# check the Kaiser-Meyer-Olkin factor adequacy
KMO(cor(dat1))
```

```{r}
# check the Bartlett's Test of Sphericity
cortest.bartlett(cor(dat1), n=500) 
```


Task 4 - Running a factor analysis
```{r}
# scree plot: how many factors do we extract?
scree(dat1, pc=F)  # F: deselect principal components since we are interested in factors
```
There are multiple approaches to interpret the scree plot and choose the number of factors to extract. One way is to look for the change in slope ('elbow'), in which case we'd choose to extract 3 factors. Another way is to retain all factors with individual eigenvalue > 1, in which case we'd choose to extract 2 factors. We're going for the second approach.

```{r}
# fit the model
fit <- factanal(dat1, factors=2, scores='regression') 
```


Task 5 - Interpreting the output
```{r}
print(fit)
```

```{r}
# another way to check the output
fit %>% tidy()
```
Commonalities of each item
For V1: 1 - uniqueness = 1 - .288 = .712
For V2: 1 - uniqueness = 1 - .223 = .777
For V3: 1 - uniqueness = 1 - .095 = .905
For V4: 1 - uniqueness = 1 - .456 = .544
For V5: 1 - uniqueness = 1 - .120 = .880
For V6: 1 - uniqueness = 1 - .106 = .894

(Cumulative) Variance explained by the 2 factors: 0.785 

The first output suggests there is no cross-loadings (i.e., Factor 2 do not load into V1-V3 items and Factor 1 does not load into V4-V6).

```{r}
# Extracting statistics
fit$STATISTIC #Chi sq

fit$PVAL # p value
```

```{r}
# Dataframe containing the factor score for each factor, for each person
scores <- fit$scores %>% as.data.frame()
```

```{r}
scores <- scores %>% mutate(Correlation=cor())
```


Extension task
# If somebody scored the following standard scores on V1 through V6, what would their factor scores for each factor be? 1,2,1,4,3,3. 

HINT: you can use tidy() to make items from the fit object easier to access.
```{r}
fit %>% tidy()
```
The individual's Factor 1 Score:
Item1_f1Loading * (Item1) + Item2_f1Loading * (Item2) + Item3_f1Loading * (Item3) + Item4_f1Loading * (Item4) + Item5_f1Loading * (Item5) + Item6_f1Loading * (Item6)  
= 0.843 * 1 + 0.877 * 2 + 0.952 * 1 -0.025 * 4 + 0.043 * 3 + 0.022 * 3
= 3.644


The individual's Factor 2 Score:
Item1_f2Loading * (Item1) + Item2_f2Loading * (Item2) + Item3_f2Loading * (Item3) + Item4_f2Loading * (Item4) + Item5_f2Loading * (Item5) + Item6_f2Loading * (Item6)  
= 0.021 * 1 + 0.086 * 2 -0.001 * 1 + 0.737 * 4 + 0.937 * 3 + 0.945 * 3
= 8.786





